Check Coverage

### 2019-11-21 analysis/merge_data.Rmd
First attempt at correction via a simple glm.

>>>>

#Correct FD for species richness

First for one study, 311
```{r}
model_data <- fd_table %>% filter(metric == "FRic", study_id == 311)
fit <- glm(value ~ year + richness, data = model_data)

pred_vars <- model_data %>% 
  select(richness, year) %>% 
  distinct() %>%
  mutate(fric_pred = predict(fit, ., type = "response"))

plot_data <- left_join(model_data, pred_vars) %>%
  mutate(fric_adj = value - fric_pred,
         fric_adj = ifelse(fric_adj > 0, fric_adj, 0))

plot_data %>%
  ggplot() +
  geom_line(aes(x = year, y = value), color = "blue") +
  geom_line(aes(x = year, y = fric_pred), color = "red") +
  geom_line(aes(x = year, y = fric_adj), color = "black") +
  scale_x_continuous(breaks = scales::pretty_breaks()) +
  theme(legend.position = "none") +
  ylab("Fric")
```
